Between Subgraph Isomorphism and Maximum Common Subgraph

### 2016-08-13 paper/paper.tex
More experimental notation.

@@

\section{Some Maths}

A non-induced subgraph isomorphism from a graph $P$ to a graph $T$ is an injective mapping from
$\operatorname{V}(P)$ to $\operatorname{V}(T)$ which maps adjacent vertices to adjacent vertices. An
induced subgraph isomorphism additionally maps non-adjacent vertices to non-adjacent vertices.

@@

We define a subgraph-except-$k$ isomorphism from $P$ to $T$ to be a subgraph isomorphism from all
but $k$ vertices of $P$ to $T$; this may be non-induced or induced, written $P[-k] \rightarrowtail
T$ and $P[-k] \hookrightarrow T$ respectively.

@@

The following propositions hold for both non-induced and induced subgraph-except-$k$ isomorphisms.

\begin{proposition}
    If $p \mapsto t$ then $\operatorname{deg}(p) \le \operatorname{deg}(t) + k$.
\end{proposition}

>>>>

%to do comments
\usepackage{color}
\newcommand{\todo}[1]{{\color{red} {[}{#1}{]}}}

@@

\section{Some Maths}
A non-induced subgraph isomorphism from a graph $P$ to a graph $T$ is an injective mapping
$i: P \rightarrowtail T $ which maps adjacent vertices to adjacent vertices. An induced subgraph
isomorphism $i: P \hookrightarrow T$, additionally maps non-adjacent vertices to non-adjacent
 vertices.

@@

We define a subgraph-except-$k$ isomorphism from $P$ to $T$ to be a subgraph isomorphism from all
but $k$ vertices of $P$ to $T$; this may be non-induced or induced, written
$i_{k}: P \rightarrowtail T$ and $i_{k}: P \hookrightarrow T$ respectively.

@@

\todo{Define $\preceq$, deg, nds, paths}

\begin{proposition}
    Let $p$ be a vertex of $P$ and $t$ a vertex in $T$. For both non-induced and induced
    subgraph-except-$k$ isomorphisms, if $i_{k}(p) = t$ then
    $\operatorname{deg}(p) \le \operatorname{deg}(t) + k$.
\end{proposition}

\begin{proposition}
    More powerfully, if $i_{k}(p) = t$ then $\operatorname{nds}(p)[k, k+1, \ldots] \preceq
    \operatorname{nds}(t)$.
\end{proposition}

As well as reasoning about degrees, we can also reason about paths.

\begin{proposition}
    If $i_{k}(p) = t$ and $i_{k}(q) = u$ then $\operatorname{paths}(p, q, 2) \le
    \operatorname{paths}(t, u, 2) + k$.
\end{proposition}

This leads to the following:

\begin{proposition}
    For a graph $G$, let $G^{n, \ell}$ be the graph with vertex set $\operatorname{V}(G)$, and
    and $p,q\in\operatorname{V}(G)$, with $p$ and $q$ adjacent if there are at least $n$
    simple paths of length exactly $\ell$ between $p$ and $q$ in $G$. Then any subgraph-except-$k$
    isomorphism $i_{k}: P \rightarrowtail T$ induces a new subgraph-except-$k$ isomorphism
    $i^{n, 2}_{k} : P^{n, 2}\rightarrowtail T^{n - k, 2}$.
\end{proposition}
